Naturalness in U(1) extensions of the MSSM

### 2015-01-15 paper/e6ssm-tuning-paper.tex
Started adding detailed discussion about the plots where we vary the cutoff.OH

To examine this further we also looked at how the tuning compares between the MSSM and E6SSM As is shown in Fig.~\ref{} the tuning in the MSSM becomes larger
than that of the E$_6$SSM when the cutoff scale is ?

>>>>

To further illustrate point we looked at how the tuning compares for a
low tuning benchmarks in the MSSM and E6SSM when the highscale
boundary condition, $M_X$ is raised.  The results of this are shown in
Fig.~\ref{Fig:BMs-varyMX} where in the top panel we see that in this
case the dependence of the E6SSM tuning on the cutoff is rather
complicated leading, such that any statement about which model is more
tuned depends on the cutoff scale considered.

The complicated shape of the E6SSM fine tuning curve can be understood
by looking at the indivual sensitivities shown in bottom left panel.
In this case one can see that the tuning is initially dominated by the
$\Delta_\lambda$ sensitivity, which contains some terms proprtional to
$M_Z^{\prime \, 2}$.  As the cutoff scale is raised however fine
tuning contributions from the stops and gluino start to feed into the
sensitivities, in particular $\Delta_{m_{H_u}^}2$ and $\Delta_\lamda$.
In the latter these contribution have the opposite sign to those from
$M_Z^\prime$ leading to this strange behaviour where $\Delta_\lambda$
passes through zero.  However in $\Delta_{m_{H_u}^}2$ dominating at
larger values of the cutoff scale we see the effect of the more common
fine tuning problem where the stops add large contributions to
$m_{H_u}^2$ , in this case leading to a large cancellation between
$m_{H_u}^2(M_X)$ and $m_{Q_3}^2(M_X)$ inside $m_{H_u}^2(M_{SUSY})$.

In the MSSM the panel on the bottom right shows that the largest
tuning contributions come from $\Delta_{A_t}$ and $\Delta_{m_{H_u}^2}$
with the former being the larger sensitivity until $M_X\approx 10^8$
at which point $\Delta_{m_{H_u}^2}$ takes over.

In this particular case the fine tuning of the E$_6$SSM benchmark becomes larger than that od the MSSM benchmark when $M_X\approx 10^{10}-10^{11}$ GeV. This is diue to ? large A_t mixing?, $M_3$? different RGEs?

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_fixed_at_ms_tuning_plot.png}}\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}%%
\caption{Top Panel: Scatter plot of fine tuning vs high scale $M_X$ for benchmark points given in (?).  Left Panel: Individual sensitivites of E6SSM BM plotted against the high scale $M_X$.  Right Panel: Individual sensitivites of MSSM BM plotted against the high scale $M_X$.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}
